Call libraries

```{r}
library(tidyr)
library(stringr)
library(dplyr)
library(plotly)
library(factoextra)
library(cluster)
library(fpc)
library(corrplot)
```

Pick up data

```{r}

bmt = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/BmtSupplierList.csv', sep=',', stringsAsFactors = FALSE)
bmt$site = 'Bmt'

krl = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/KrlSupplierList.csv', sep=',', stringsAsFactors = FALSE)
krl$site = 'Krl'

srn = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/SrnSupplierList.csv', sep=',', stringsAsFactors = FALSE)
srn$site = 'Srn'

strth = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/StrthSupplierList.csv', sep=',', stringsAsFactors = FALSE)
strth$site = 'Strth'

str(bmt)

str(krl)

str(srn)

str(strth)

```

Combine datasets

```{r}
sites = rbind(mbt, krl, srn, strth)
sites$eCat_Flag = ifelse(sites$eCat_Flag =='eCat', 'eCat', 'Non eCat')
table(sites$eCat_Flag)
str(sites)
```

Appreciate proportion of onboarded suppliers for Bmt and Krl and distribution of the GMSG variable

```{r}
p = sites %>% filter(sites$site == 'Krl' | sites$site == 'Bmt') %>% group_by(eCat_Flag) %>% summarise(count = n()) %>% plot_ly(labels = ~eCat_Flag, values = ~count) %>% add_pie(hole = 0.6)
p

p = sites %>% group_by(Main_GMSG) %>% summarise(count = n()) %>% plot_ly(x = ~Main_GMSG, y = ~count, type = 'bar') %>%layout( barmode = 'stack')
p

```

Boxplot spend per site

```{r}
p = plot_ly(sites, y = ~Sum_of_PO_Amt_USD, color = ~site,  x = ~site, type = 'box')
p
```

Boxplot transactions per site

```{r}
p = plot_ly(sites, y = ~Count_of_PO_Num, color = ~site,  x = ~site, type = 'box')
p
```

```{r}
p = plot_ly(sites, x = ~Count_of_PO_Num, y = ~Sum_of_PO_Amt_USD, color = ~Calloff_Trans)
p

```

Identify correlations between varialbes

```{r}
temp1 = sites
temp1 = temp1 %>% filter(temp1$site == 'Bmt' | temp1$site == 'Krl')
str(temp1)
temp1$eCatTemp = ifelse(temp1$eCat_Flag == 'eCat', 1, 0)
temp1$eCat_Flag = NULL
temp1$VN = NULL
temp1$Vendor_Name_VN = NULL
temp1$Main_GMSG = NULL
temp1$site = NULL
str(temp1)
mcor = cor(temp1)
mcor

corrplot(mcor, type = 'upper', order = 'hclust', tl.col = 'black', tl.srt = 45)

```


Identify outliers per spend (interquartiles method)

```{r}

quantiles = quantile(sites$Sum_of_PO_Amt_USD, probs = c(.25, .75))
str(quantiles)
range = 1.5 * IQR(sites$Sum_of_PO_Amt_USD)
range
normal_gdp = subset(sites, sites$Sum_of_PO_Amt_USD > (quantiles[1] - range) & sites$Sum_of_PO_Amt_USD < (quantiles[2] + range))
str(normal_gdp)
```

Identify outliers per transactions (interquartiles method)

```{r}

quantiles = quantile(normal_gdp$Count_of_PO_Num, probs = c(.25, .75))
str(quantiles)
range = 1.5 * IQR(normal_gdp$Count_of_PO_Num)
range
normal_gdp = subset(normal_gdp, normal_gdp$Count_of_PO_Num > (quantiles[1] - range) & normal_gdp$Count_of_PO_Num < (quantiles[2] + range))
str(normal_gdp)

```

Boxplot spend per site

```{r}
p = plot_ly(normal_gdp, y = ~Sum_of_PO_Amt_USD, color = ~site,  x = ~site, type = 'box')
p
```

Boxplot transactions per site

```{r}
p = plot_ly(normal_gdp, y = ~Count_of_PO_Num, color = ~site,  x = ~site, type = 'box')
p
```


```{r}
p = plot_ly(normal_gdp, x = ~Count_of_PO_Num, y = ~Sum_of_PO_Amt_USD, color = ~Calloff_Trans)
p

```

Plot proportion of onboarded suppliers for Bmt and Krl and GMSG variable distribution

```{r}
p = normal_gdp %>% filter(normal_gdp$site == 'Krl' | normal_gdp$site == 'Bmt') %>% group_by(eCat_Flag) %>% summarise(count = n()) %>% plot_ly(labels = ~eCat_Flag, values = ~count) %>% add_pie(hole = 0.6)
p

p = normal_gdp %>% group_by(Main_GMSG) %>% summarise(count = n()) %>% plot_ly(x = ~Main_GMSG, y = ~count, type = 'bar') %>%layout( barmode = 'stack')
p

```

Identificar correlaciones entre variables

```{r}
temp1 = normal_gdp
temp1 = temp1 %>% filter(temp1$site == 'Bmt' | temp1$site == 'Krl')
str(temp1)
temp1$eCatTemp = ifelse(temp1$eCat_Flag == 'eCat', 1, 0)
temp1$eCat_Flag = NULL
temp1$VN = NULL
temp1$Vendor_Name_VN = NULL
temp1$Main_GMSG = NULL
temp1$site = NULL
str(temp1)
mcor = cor(temp1)
mcor

corrplot(mcor, type = 'upper', order = 'hclust', tl.col = 'black', tl.srt = 45)

```

Generate new files without outliers

```{r}
BmtSupplierList2 = normal_gdp %>% filter(normal_gdp$site == 'Bmt') %>% mutate(site = NULL)
write.csv(BmtSupplierList2, file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/BmtSupplierList2.csv', row.names = FALSE)

KrlSupplierList2 = normal_gdp %>% filter(normal_gdp$site == 'Krl') %>% mutate(site = NULL)
write.csv(KrlSupplierList2, file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/KrlSupplierList2.csv', row.names = FALSE)

SrnSupplierList2 = normal_gdp %>% filter(normal_gdp$site == 'Srn') %>% mutate(site = NULL)
write.csv(SrnSupplierList2, file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/SrnSupplierList2.csv', row.names = FALSE)

StrthSupplierList2 = normal_gdp %>% filter(normal_gdp$site == 'Strth') %>% mutate(site = NULL)
write.csv(StrthSupplierList2, file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/StrthSupplierList2.csv', row.names = FALSE)

```




