Call libraries

```{r}
library(tidyr)
library(stringr)
library(dplyr)
library(plotly)
library(factoextra)
library(cluster)
library(fpc)
```



Pick up datasets

```{r}

bmt = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/BmtSupplierList.csv', sep=',', stringsAsFactors = FALSE)

krl = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/KrlSupplierList.csv', sep=',', stringsAsFactors = FALSE)

srn = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/SrnSupplierList.csv', sep=',', stringsAsFactors = FALSE)

strth = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/StrthSupplierList.csv', sep=',', stringsAsFactors = FALSE)

str(bmt)

str(krl)

str(srn)

str(strth)

```

Combine Bmt y Krl

```{r}
pilot = rbind(bmt, krl) %>% mutate(eCat_Flag = ifelse(eCat_Flag == 'eCat', 1, 0)) %>% mutate(eCat_Flag = as.integer(eCat_Flag)) 
str(pilot)
set.seed(999)
pilot = pilot[sample(1:nrow(pilot)),]
str(pilot)
```

Remove variables from datasets

```{r}

pilotNums = pilot %>% mutate(VN = NULL, Vendor_Name_VN = NULL, Price_Range = NULL, BuySmart_Usage = NULL, Main_GMSG = NULL)
str(pilotNums)
table(pilotNums$eCat_Flag)

testing1 = sarnia %>% mutate(VN = NULL, Vendor_Name_VN = NULL, eCat_Flag = NULL, Price_Range = NULL, BuySmart_Usage = NULL, Main_GMSG = NULL)
str(testing1)

testing2 = strathcona %>% mutate(VN = NULL, Vendor_Name_VN = NULL, eCat_Flag = NULL, Price_Range = NULL, BuySmart_Usage = NULL, Main_GMSG = NULL)
str(testing2)

```

Scale and plot elbow chart through kmeans method

```{r}
set.seed(1234)
pilotscaled = scale(pilotNums)
summary(pilotscaled)

n.clusters <- 14
wss <- (nrow(pilotscaled)-1)*sum(apply(pilotscaled,2,var))
for (i in 2:n.clusters){
  wss[i] <- sum(kmeans(pilotscaled,centers=i)$withinss)
}

plot(1:n.clusters, wss, type="b", xlab="Number of clusters",
     ylab="WCV",
     main="Quantity of clusters per variation ",
     pch=20, cex=2)

```

Plot WCV to confirm number of clusters

```{r}
n.clusters <- 14
wss <- (nrow(pilotscaled)-1)*sum(apply(pilotscaled,2,var))
for (i in 2:n.clusters){
  wss[i] <- sum(kmeans(pilotscaled,centers=i)$betweenss)
}

plot(1:n.clusters, wss, type="b", xlab="Number of clusters",
     ylab="WCV",
     main="Quantity of clusters per variation ",
     pch=20, cex=2)

```

Cluster with c=6

```{r}
fit <- kmeans(pilotscaled, centers=6, iter.max = 1000)
aggregate(pilotscaled,by=list(fit$cluster),FUN=mean)
print(fit)
fit$withinss
boxplot(pilotNums$Calloff_Trans ~fit$cluster)


```
Incorporate clustering column to dataset before balancing

```{r}
str(pilot)
pilot = data.frame(pilot, fit$cluster)
pilot$fit.cluster = as.factor(pilot$fit.cluster)
str(pilot)

```

Balance based on eCat_Flag variable and divide dataset in training and validation

```{r}

positiveclassIxs = which(pilot$eCat_Flag == 1)
negativeclassIxs = which(pilot$eCat_Flag == 0)

PropPositives = length(positiveclassIxs) / nrow(pilot)

positiveclassIxs.sample = sample(positiveclassIxs, floor(0.7 * nrow(pilot) * PropPositives))
str(positiveclassIxs.sample)
negativeclassIxs.sample = sample(negativeclassIxs, floor(0.7 * nrow(pilot) * (1 - PropPositives)))
str(negativeclassIxs.sample)

trainingIndex = c(positiveclassIxs.sample, negativeclassIxs.sample)
validacionIndex = seq_len(nrow(pilot))[!seq_len(nrow(pilot)) %in% trainingIndex]

trainingpilot = pilot[trainingIndex, ]
table(trainingpilot$eCat_Flag)
validacionpilot = pilot[validacionIndex, ]
table(validacionpilot$eCat_Flag)

```

Model with ligistic regression

```{r}
ecuation = 'eCat_Flag~Sum_of_PO_Amt_USD+Count_of_PO_Num+Calloff_Spend+Calloff_Trans+MRP_Requisition_Ratio+Min_Price+Max_Price'
modeloLog = glm(ecuation, binomial(link='logit'),data=trainingpilot)
summary(modeloLog)

prediccion1 = predict(modeloLog, validacionpilot, type='response')
str(prediccion1)

modelo1 = data.frame(validacionpilot, prediccion1)
str(modelo1)

```

Remodel with logistic regression but only with higher weight variables

```{r}
ecuation = 'eCat_Flag~Sum_of_PO_Amt_USD+Calloff_Trans+Max_Price'
modeloLog = glm(ecuation, binomial(link='logit'),data=trainingpilot)
summary(modeloLog)

prediccion1 = predict(modeloLog, validacionpilot, type='response')
str(prediccion1)

modelo1 = data.frame(validacionpilot, prediccion1)
str(modelo1)

```

Calculate metrics to determine best probability threshdold

```{r}

real = data.frame(validacionpilot$eCat_Flag)
pred = data.frame(prediccion1)

confusion = data.frame(real, pred, valoracion = '', evaluacion = '')
i = 1
matrizconf = data.frame(umbral2 = double(), accurracy = double(), precision = double(), sensibilidad = double(), especificidad = double())

for (umbral in seq(0, 1, 0.05)){

confusion$valoracion = ifelse(confusion$prediccion1 > umbral, 1, 0)

confusion = confusion %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 1 & valoracion == 1, 'VP', evaluacion))%>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 1 & valoracion == 0, 'FN', evaluacion)) %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 0 & valoracion == 1, 'FP', evaluacion)) %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 0 & valoracion == 0, 'VN', evaluacion))

vp =  length(which(confusion$evaluacion == 'VP'))
fn =  length(which(confusion$evaluacion == 'FN'))
fp =  length(which(confusion$evaluacion == 'FP'))
vn =  length(which(confusion$evaluacion == 'VN'))
total = length(confusion$evaluacion)

accuracy = (vp + vn) / total
precision = vp / (vp + fp)
sensibilidad = vp / (vp + fn)
especificidad = vn / (fp + vn)

c = c(umbral, accuracy, precision, sensibilidad, especificidad)

matrizconf[i, ] = c
i = i + 1
}

matrizconf

```

Plot all metrics

```{r}
p = plot_ly(matrizconf, x = ~umbral2, y = ~sensibilidad, mode = 'lines+markers', name = 'sensibilidad', type = 'scatter') %>% add_trace(x = ~umbral2, y = ~especificidad, name = 'especificidad', mode = 'lines+markers') %>% add_trace(x = ~umbral2, y = ~accuracy, name = 'accuracy', mode = 'lines+markers') %>% add_trace(x = ~umbral2, y = ~precision, name = 'precision', mode = 'lines+markers', color = I('black'))
p

```

Plot ROC Curve

```{r}
p = plot_ly(matrizconf, x = ~especificidad, y = ~sensibilidad, type = 'scatter', mode = 'lines+markers') %>% add_segments(x = 0, xend = 1, y = 0, yend = 1) %>% layout(showlegend = FALSE) %>% layout(title = 'Curva ROC')
p
```

According to cut point between specificity and sensibility curves and confirming with the ROC curve, the optimal probability threshdold is 0.057

Calculate RMSE

```{r}
estimacion = data.frame(validacionpilot$eCat_Flag, prediccion1)
estimacion$estimado = ifelse(estimacion$prediccion1 >= 0.057, 1, 0)
str(estimacion)

RMSE = sqrt(mean((estimacion$validacionpilot.eCat_Flag - estimacion$estimado)^2))
paste('RMSE =', round(RMSE, 4), sep = ' ')

```

Calculate confusion matrix metrics according to selected threshdold

```{r}

real = data.frame(validacionpilot$eCat_Flag)
pred = data.frame(prediccion1)

confusion = data.frame(real, pred, valoracion = '', evaluacion = '')

matrizconf = data.frame(umbral2 = double(), accurracy = double(), precision = double(), sensibilidad = double(), especificidad = double())

confusion$valoracion = ifelse(confusion$prediccion1 >= 0.057, 1, 0)

confusion = confusion %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 1 & valoracion == 1, 'VP', evaluacion))%>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 1 & valoracion == 0, 'FN', evaluacion)) %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 0 & valoracion == 1, 'FP', evaluacion)) %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 0 & valoracion == 0, 'VN', evaluacion))

vp =  length(which(confusion$evaluacion == 'VP'))
fn =  length(which(confusion$evaluacion == 'FN'))
fp =  length(which(confusion$evaluacion == 'FP'))
vn =  length(which(confusion$evaluacion == 'VN'))
total = length(confusion$evaluacion)

accuracy = (vp + vn) / total
precision = vp / (vp + fp)
sensibilidad = vp / (vp + fn)
especificidad = vn / (fp + vn)

paste('Accuracy =', round(accuracy, 4), sep = ' ')
paste('Precision =', round(precision, 4), sep = ' ')
paste('Sensibilidad =', round(sensibilidad, 4), sep = ' ')
paste('Especificidad =', round(especificidad, 4), sep = ' ')
```


