
Call libraries

```{r}
library(tidyr)
library(stringr)
library(dplyr)
library(plotly)
library(factoextra)
library(cluster)
library(fpc)
library(rpart)
library(rpart.plot)
```

Pick up datasets

```{r}

bmt = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/BmtSupplierList.csv', sep=',', stringsAsFactors = FALSE)

krl = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/KrlSupplierList.csv', sep=',', stringsAsFactors = FALSE)

srn = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/SrnSupplierList.csv', sep=',', stringsAsFactors = FALSE)

strth = read.csv(file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/StrthSupplierList.csv', sep=',', stringsAsFactors = FALSE)

str(bmt)

str(krl)

str(srn)

str(strth)

```

Combine Bmt y Krl

```{r}
pilot = rbind(bmt, kearl) %>% mutate(eCat_Flag = ifelse(eCat_Flag == 'eCat', 1, 0)) %>% mutate(eCat_Flag = as.integer(eCat_Flag)) 
str(pilot)
set.seed(999)
pilot = pilot[sample(1:nrow(pilot)),]
str(pilot)
```

Remove variables from datasets

```{r}

pilotNums = pilot %>% mutate(VN = NULL, Vendor_Name_VN = NULL, Price_Range = NULL, BuySmart_Usage = NULL, Main_GMSG = NULL)
str(pilotNums)
table(pilotNums$eCat_Flag)

testing1 = sarnia %>% mutate(VN = NULL, Vendor_Name_VN = NULL, eCat_Flag = NULL, Price_Range = NULL, BuySmart_Usage = NULL, Main_GMSG = NULL)
str(testing1)

testing2 = strathcona %>% mutate(VN = NULL, Vendor_Name_VN = NULL, eCat_Flag = NULL, Price_Range = NULL, BuySmart_Usage = NULL, Main_GMSG = NULL)
str(testing2)

```

Scale and plot elbow chart for PAM

```{r}
set.seed(678901)
pilotscaled = scale(pilotNums)
summary(pilotscaled)

fviz_nbclust(pilotscaled, pam, method = 'wss')

```

Method average silhouette for PAM to confirm the number of clusters

```{r}
fviz_nbclust(pilotscaled, pam, method = 'silhouette')

```

Cluster with PAM with c=6

```{r}

m.gower = daisy(pilotscaled, metric = c('gower'), stand = TRUE)
pam.res = pam(m.gower, 6)
str(pam.res)

aggregate(pilotscaled,by=list(pam.res$clustering),FUN=mean)
pam.res$medoids
boxplot(pilotNums$Calloff_Trans ~pam.res$clustering)

```

Plot pilot dataset based on clusters, size of dots based on calloff transactions

```{r}
pilotscaled2 = data.frame(pilotscaled)
pilotscaled2$clusters = pam.res$clustering 
p = plot_ly(pilotscaled2, x = ~Sum_of_PO_Amt_USD, y = ~Count_of_PO_Num, mode = 'markers', name = ~clusters, type = 'scatter', color = ~clusters, size = ~Calloff_Spend) %>% layout(title = 'Clustering scaled c=6 PAM, spend vs trans, calloff spend')
p

```

Incorporate clustering column to dataset before balancing

```{r}
pilot = data.frame(pilot, pam.res$clustering)
str(pilot)

```

Balance based on eCat_Flag variable and divide dataset in training and validation

```{r}

positiveclassIxs = which(pilot$eCat_Flag == 1)
negativeclassIxs = which(pilot$eCat_Flag == 0)

PropPositives = length(positiveclassIxs) / nrow(pilot)

positiveclassIxs.sample = sample(positiveclassIxs, floor(0.7 * nrow(pilot) * PropPositives))
str(positiveclassIxs.sample)
negativeclassIxs.sample = sample(negativeclassIxs, floor(0.7 * nrow(pilot) * (1 - PropPositives)))
str(negativeclassIxs.sample)

trainingIndex = c(positiveclassIxs.sample, negativeclassIxs.sample)
validacionIndex = seq_len(nrow(pilot))[!seq_len(nrow(pilot)) %in% trainingIndex]

trainingpilot = pilot[trainingIndex, ]
table(trainingpilot$eCat_Flag)
validacionpilot = pilot[validacionIndex, ]
table(validacionpilot$eCat_Flag)

```

Train decision tree

```{r}
fmla = 'eCat_Flag~Sum_of_PO_Amt_USD+Count_of_PO_Num+Calloff_Spend+Calloff_Trans+MRP_Requisition_Ratio+Min_Price+Max_Price'
arbol = rpart(fmla, data = trainingpilot)
arbol
```

Plot decision tree

```{r}
rpart.plot(arbol, fallen.leaves = FALSE, type = 2)
```

Predict with decision tree

```{r}
prediccionarbol = predict(arbol, validacionpilot, type = 'vector')
predict1 = data.frame(prediccionarbol)
str(predict1)
```

Calculate metrics to determine the best probability threshdold

```{r}

real = data.frame(validacionpilot$eCat_Flag)
pred = predict1

confusion = data.frame(real, pred, valoracion = '', evaluacion = '')

i = 1
matrizconf = data.frame(umbral2 = double(), accurracy = double(), precision = double(), sensibilidad = double(), especificidad = double())
str(matrizconf)

for (umbral in seq(0, 1, 0.05)){

confusion$valoracion = ifelse(confusion$prediccionarbol > umbral, 1, 0)

confusion = confusion %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 1 & valoracion == 1, 'VP', evaluacion))%>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 1 & valoracion == 0, 'FN', evaluacion)) %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 0 & valoracion == 1, 'FP', evaluacion)) %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 0 & valoracion == 0, 'VN', evaluacion))

vp =  length(which(confusion$evaluacion == 'VP'))
fn =  length(which(confusion$evaluacion == 'FN'))
fp =  length(which(confusion$evaluacion == 'FP'))
vn =  length(which(confusion$evaluacion == 'VN'))
total = length(confusion$evaluacion)

accuracy = (vp + vn) / total
precision = vp / (vp + fp)
sensibilidad = vp / (vp + fn)
especificidad = vn / (fp + vn)

c = c(umbral, accuracy, precision, sensibilidad, especificidad)

matrizconf[i, ] = c
i = i + 1
}

matrizconf

```

Plot all metrics

```{r}
p = plot_ly(matrizconf, x = ~umbral2, y = ~sensibilidad, mode = 'lines+markers', name = 'sensibilidad', type = 'scatter') %>% add_trace(x = ~umbral2, y = ~especificidad, name = 'especificidad', mode = 'lines+markers') %>% add_trace(x = ~umbral2, y = ~accuracy, name = 'accuracy', mode = 'lines+markers') %>% add_trace(x = ~umbral2, y = ~precision, name = 'precision', mode = 'lines+markers', color = I('black'))
p

```

Plot ROC Curve

```{r}
p = plot_ly(matrizconf, x = ~especificidad, y = ~sensibilidad, type = 'scatter', mode = 'lines+markers') %>% add_segments(x = 0, xend = 1, y = 0, yend = 1) %>% layout(showlegend = FALSE) %>% layout(title = 'Curva ROC')
p
```

According to cut point between specificity and sensibility curves and confirming with the ROC curve, the optimal probability threshdold is 0.037

Calculate RMSE

```{r}
estimacion = data.frame(validacionpilot$eCat_Flag, predict1$prediccionarbol)
str(estimacion)
estimacion$estimado = ifelse(estimacion$predict1.prediccionarbol >= 0.037, 1, 0)
str(estimacion)

RMSE = sqrt(mean((estimacion$validacionpilot.eCat_Flag - estimacion$predict1.prediccionarbol)^2))
paste('RMSE =', round(RMSE, 4), sep = ' ')

```

Calculate confusion matrix metrics according to selected threshdold

```{r}

real = data.frame(validacionpilot$eCat_Flag)
pred = data.frame(predict1)

confusion = data.frame(real, pred, valoracion = '', evaluacion = '')

matrizconf = data.frame(umbral2 = double(), accurracy = double(), precision = double(), sensibilidad = double(), especificidad = double())

confusion$valoracion = ifelse(confusion$prediccionarbol >= 0.037, 1, 0)

confusion = confusion %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 1 & valoracion == 1, 'VP', evaluacion))%>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 1 & valoracion == 0, 'FN', evaluacion)) %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 0 & valoracion == 1, 'FP', evaluacion)) %>% mutate(evaluacion = ifelse(validacionpilot.eCat_Flag == 0 & valoracion == 0, 'VN', evaluacion))

vp =  length(which(confusion$evaluacion == 'VP'))
fn =  length(which(confusion$evaluacion == 'FN'))
fp =  length(which(confusion$evaluacion == 'FP'))
vn =  length(which(confusion$evaluacion == 'VN'))
total = length(confusion$evaluacion)

accuracy = (vp + vn) / total
precision = vp / (vp + fp)
sensibilidad = vp / (vp + fn)
especificidad = vn / (fp + vn)

paste('Accuracy =', round(accuracy, 4), sep = ' ')
paste('Precision =', round(precision, 4), sep = ' ')
paste('Sensibilidad =', round(sensibilidad, 4), sep = ' ')
paste('Especificidad =', round(especificidad, 4), sep = ' ')
```

By comparing metrics of the two models of logistic regression, the decision tree model shows beter performance

Predecir con los datasets de Srn y Strth (testing)


```{r}
predprobsrn = predict(arbol, srn, type = 'vector')
predprobstrth = predict(arbol, strth, type = 'vector')

SrnPrediccion = data.frame(srn, predprobsrn)
SrnPrediccion$prediccion = ifelse(SrnPrediccion$predprobsrn >= 0.037, 1, 0)
table(SrnPrediccion$prediccion)

write.csv(SrnPrediccion, file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/SrnPrediccion.csv')

StrthPrediccion = data.frame(strth, predprobstrth)
StrthPrediccion$prediccion = ifelse(StrthPrediccion$predprobstrth >= 0.037, 1, 0)
table(StrthPrediccion$prediccion)

write.csv(strthPrediccion, file = 'C:/Users/Esteban Guerrero/Documents/Data Science EGB/Proyecto Final/StrthPrediccion.csv')
```

